Solution-aware vs global ReLU selection: \\ partial MILP strikes back for DNN verification

### 2025-01-30 CAV 2025 TODO/Comparison.tex
comp

		\draw[->, thick] (hidden1) -- (hidden3) node[midway, above] {ReLU?};
		%\draw[->, thick] (hidden2) -- (hidden4);

@@

We call {\em global scoring} (GS) such functions $s_{FSB},s_{SR}$  because they score ReLUs as accuratly as possible, considering that they do not have access to the solution $sol(a),sol(b)$ values. This analysis already hints at our novel ranking function, that will be solution-aware to be more accurate.

>>>>

		\draw[->, thick] (hidden1) -- (hidden3) node[midway, above] {open ReLU?};
		%\draw[->, thick] (hidden2) -- (hidden4);

@@

We call {\em global scoring} (GS) such functions $s_{FSB},s_{SR}$  because they score ReLUs as accuratly as possible, considering that they do not have access to the solution values $sol(a),sol(b)$. This analysis already hints at our novel ranking function, that will be solution-aware to be more accurate.
